Untitled

### 2020-07-31 Thesis_Chapter_1/Supp_Material.Rmd
edits in captions. One extra table added

__Table S2.__ Numerical values of all the traits measured for each species.

__Table S3.__ Seed set in percentage for hand cross-pollination, hand self-pollination, natural selfing and apomixis for all species.

__Table S4.__ Total number of pollen grains per stigma.

__Table S5.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.

__Table S6.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.

__Table S7.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.

@@

__Table S9.__ Phylogenetic signal and significance for all the different traits

@@

__Figure S2__. Total amount of pollen deposited per stigma.

__Figure S3__. Pollen ratios for the different recipient species.

__Figure S4__. Pollen ratios for the different recipient species by family.

__Figure S5__. Statistical comparison of the pollen ratios by family.

@@

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Trait measurements ($\\bar{X}$ ± SD) for the 13 different traits measured for each plant species. Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods. ", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
```

@@

```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
library(kableExtra)
dat <- readRDS("Tables/total_pollen.rds")
dat <- dat[,-5]
colnames(dat) <- c("Recipient", "Donor", "Recipient pollen grains", "Donor pollen grains")

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average pollen grains per stigma for both recipient and donor species for 20 different treatments (3 replicates per treatment)", escape = FALSE,booktabs = T,linesep = "\\addlinespace")

@@

kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models. The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control. Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
```

@@

kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments. We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept). The first species on the row names are the pollen recipient species and the second species the pollen donor species. Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses") %>%
  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>%column_spec(1,italic =T)%>% row_spec(0,bold=TRUE)
```

@@

kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with 100\\% foreign pollen (N=900). From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events. In this table we show just the treatments that lead to seed production.") %>% kable_styling(font_size = 10,position="left",full_width=F,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>%
   add_footnote("*            Note: There are some specific cases that we think that hybridization did not occur and that the recipient species were pollen contaminated, like the one of C. annuum with S. alba with 127 seeds. This seems to be the case for 5 other crosses that had very low seed production when they were pollinated with 100% foreign pollen with species of other family members. This represents very few isolated cases (0.67% of all the 100% foreign pollen crosses conducted) and we think that our results are not compromised by this fact. ", notation = "none") %>% column_spec(1,italic =T)%>% column_spec(2,italic =T)

>>>>

__Table S2.__ Trait measurements for all species.

__Table S3.__ Seed:ovule ratio (%) of the different reproductive biology treatments.

__Table S4.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.

__Table S5.__ Summary of the effect from the linear models of the different pollen donors on each recipient species.

__Table S6.__ Estimates, standard error, t-value and _P_-value of the effect of the different 9 donors on each recipient species.

__Table S7.__ Total number of seeds produced with the 100% foreign pollen treatments.

@@

__Table S9.__ Phylogenetic signal and significance for all the different traits.

@@

__Figure S2__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.

__Figure S3__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.

__Figure S4__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.

__Figure S5__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.

@@

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Average values of the trait measurements for each plant species. Sample sizes are provided on the methods section. Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods. The raw data can be found on the online repository provided within this manuscript.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
```

@@

```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
library(kableExtra)
dat <- readRDS("Tables/total_pollen.rds")
dat <- dat[,-5]
colnames(dat) <- c("Recipient species", "Donor species", "Recipient pollen grains", "Donor pollen grains")

kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)

@@

kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species. The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment. Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
```

@@

kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments. We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept). The first species on the row names are the pollen recipient species and the second species the pollen donor species. Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses") %>%
  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>%column_spec(1,italic =T)%>% row_spec(0,bold=TRUE)
```

@@

kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with 100\\% foreign pollen treatments (N=900). From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events. In this table we show just the treatments that lead to seed production.") %>% kable_styling(font_size = 10,position="left",full_width=F,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>%
   add_footnote("*            Note: There are some specific cases that we think that hybridization did not occur and that the recipient species were pollen contaminated, like the one of C. annuum with S. alba with 127 seeds. This seems to be the case for 5 other crosses that had very low seed production when they were pollinated with 100% foreign pollen with species of other family members. This represents very few isolated cases (0.67% of all the 100% foreign pollen crosses conducted) and we think that our results are not compromised by this fact. ", notation = "none") %>% column_spec(1,italic =T)%>% column_spec(2,italic =T)
